The \project{unRAVE} catalog of stellar atmospheric parameters and\\ chemical abundances for chemo-dynamic studies in the \gaia\ era

### 2016-09-09 article/unrave.tex
Include specifics of OC selection #32

The fourth \rave\ data release made use of a number of high-resolution studies
to verify the accuracy of the reported stellar atmospheric parameters.  These
samples include main-sequence stars, giant stars, with a particular focus to
include metal-poor stars to identify (and correct) any deviations at low
and high metallicities.  We refer the reader to \citet{Kordopatis_2013} for
the full compilation of literature sources.  Although the stellar atmospheric 
parameters in this compilation come from multiple (heterogeneous) sources, we 
find generally good agreement with these works (Figure 
\ref{fig:kordopatis-calibration}).  However, some reservation is warranted 
when evaluating this comparison, as some of the metal-poor stars in this 
calibration sample formed part of our training set.

@@

After verifying that our atmospheric parameters and abundances are comparable 
with other high-resolution studies, here we verify that the abundances we find
are consistent with expectations from astrophysics.  In the \rave\ survey, 
\cite{Anguiano_2015} identified 70 stars with positions and radial velocities that are
consistent with being members of globular clusters: 49 stars belonging to NGC~5139
($\omega$~Centauri), 11 members of the retrograde globular cluster NGC~3201, and 10 
members of NGC~362. In addition, \citet{Kunder_2014} compiled 12 stars thought to 
belong to NGC~1851, and a further 10 stars in NGC~6752.  We refer the reader to 
those studies for details regarding the membership selection.

In Figure~\ref{fig:globular-cluster-HRD} we show our effective temperature
$\teff$ and surface gravity $\logg$ for these prescribed globular cluster members.
The right-hand panels indicate measurements made in this work, and for comparison 
purposes we have included the results from the fourth \rave\ data release in the 
left-hand panels.  We show representative \project{PARSEC} isochrones 
\citep{Bressan_2012} in all panels, where the isochrone ages and metallicities 
are adopted from \citet{Kunder_2016,Marin-Franch_2009}, and the 
\citet[][accessed 6 September 2016]{Harris_1996} online catalog of globular 
cluster properties.  The globular cluster with the most number of members is 
NGC~5139 ($\omega$-Centauri), where we find a significant metallicity spread
consistent with high-resolution studies \citep{Marino_2011,Carretta_2009,Carretta_2013}. 
Based on the pre-defined membership criteria, we find the mean metallicity
of $\omega$-Centauri to be $[{\rm Fe/H}] = -0.85$.  However, it is clear that the 
membership criteria could be improved with our revised metallicities and 
detailed chemical abundances.  Indeed, our individual abundance labels could 
be used to identify globular cluster members that are now tidally disrupted 
\citep{Anguiano_2016,Kuzma_2016,Navin_2016}, even for stars with low S/N ratios.

@@

The \rave\ survey observed $\sim$160 highly probable members of several open clusters:
78 stars in the Pleiades, 26 in Hyades, 30 stars in the solar-metallicity cluster
M67, and 13 stars in IC4651. Details on the open cluster membership and selection can 
be found in \cite{Kunder_2016}.  We show the effective temperature $\teff$ and surface
gravity $\logg$ for these stars in Figure \ref{fig:open-cluster-HRD}.  The isochrones
are sourced from \citet{Bressan_2012}, with cluster properties adopted from 
\cite{Kunder_2016} and \cite{Kharchenko_2013}.

>>>>

The fourth \rave\ data release made use of a number of high-resolution studies
to verify the accuracy of their derived stellar atmospheric parameters.  These
samples include main-sequence stars, giant stars, with a particular focus to
include metal-poor stars to identify (and correct) any deviations at low
metallicities.  We refer the reader to \citet{Kordopatis_2013} for the full 
compilation of literature sources.  Although the stellar atmospheric parameters
in this compilation come from multiple (heterogeneous) sources, we find 
generally good agreement with these works 
(Figure \ref{fig:kordopatis-calibration}).  However, we note that some 
reservation is warranted when evaluating this comparison, as some of the 
metal-poor stars in this calibration sample formed part of our training set.

@@

After verifying that our atmospheric parameters and abundances are comparable 
with high-resolution studies, here we verify that our results are consistent
with expectations from astrophysics.  In the \rave\ survey, \cite{Anguiano_2015}
identified 70 stars with positions and radial velocities that are consistent 
with being members of globular clusters: 49 stars belonging to NGC~5139
($\omega$~Centauri), 11 members of the retrograde globular cluster NGC~3201, and 10 
members of NGC~362. In addition, \citet{Kunder_2014} compiled 12 stars thought to 
belong to NGC~1851, and a further 10 stars in NGC~6752.  We refer the reader to 
those studies for details regarding the membership selection.

In Figure~\ref{fig:globular-cluster-HRD} we show our effective temperature
$\teff$ and surface gravity $\logg$ for these prescribed globular cluster members.
The right-hand panels indicate measurements made in this work, and for comparison 
purposes we have included the results from the fourth \rave\ data release in the 
left-hand panels.  We show representative \project{PARSEC} isochrones 
\citep{Bressan_2012} in all panels, where the isochrone ages and metallicities 
are adopted from \citet{Kunder_2016,Marin-Franch_2009}, and the 
\citet[][accessed 6 September 2016]{Harris_1996} catalog of globular 
cluster properties.  The globular cluster with the most number of members is 
NGC~5139 ($\omega$-Centauri), where we find a significant metallicity spread
that is consistent with high-resolution studies \citep{Marino_2011,Carretta_2009,
Carretta_2013}. Based on the pre-defined membership criteria, we find the mean 
metallicity of $\omega$-Centauri to be $[{\rm Fe/H}] = -0.85$.  However, it 
is clear that the membership criteria could be improved with our revised 
metallicities and detailed chemical abundances.  Indeed, our individual abundance
labels could be further used to identify globular cluster members --- at least, of
relatively metal-rich clusters ---  that are now tidally disrupted 
\citep{Anguiano_2016,Kuzma_2016,Navin_2016}, even for stars with low S/N ratios.

@@

Using positions, proper motions, and metallicities from the \rave\ official
data release (such that they can be used as comparison), we identify $\sim$160 
probable members of four open clusters that were observed by \rave.  
Upon requiring $(\alpha,\delta) = (51.5^\circ$ to $57.5^\circ$, 21.5$^\circ$ to 28$^\circ)$,
have error in metallicity \texttt{e\_M\_H\_K} $< 0.5$~dex, and radial
velocities between $-10$~km~s$^{-1}$ and 20~km~s$^{-1}$, we identify 78 
Pleiades members.  For the Hyades, by requiring stars within $3.5^\circ$ of the
cluster centre to have: radial velocities between 36~km~s$^{-1}$ and 44~km~s$^{-1}$,
$[{\rm M/H}]_{RAVE}$ within $-0.15$ and 0.35, and \rave\ metallicity errors
$<0.12$~dex, we identify 26 potential members.  Similarly for IC4561 we select
13 stars by requiring: radial velocities within $-20$~km~s$^{-1}$ to $-40$~km~s$^{-1}$,
an error in radial velocity $<3$~km~s$^{-1}$; $[{\rm M/H}]_{RAVE}$ within $-0.15$ and 0.35;
$\alpha$ between $261.1^\circ$ and $261.6^\circ$; and $\delta$ within $-49.7^\circ$
and $-50.1^\circ$.  For the solar-metallicity open cluster member, we 30 select stars solely on
position: $(\alpha,\delta) = (133.1^\circ$ to $132.5^\circ$, $11.6^\circ$ to $12^\circ)$.
We show the effective temperature $\teff$ and surface gravity $\logg$ for these
cluster candidates in Figure \ref{fig:open-cluster-HRD}.  The isochrones are 
sourced from \citet{Bressan_2012}, with cluster properties adopted from 
\cite{Kharchenko_2013}.
